\LARGE\singlespacing{\textbf{S1 Appendix} \\ \medskip Transmission of respiratory viral infections with and without air cleaners in a Swiss school under non-pandemic conditions in 2023: A modeling study of epidemiological, environmental, and molecular data}

### 2023-10-03 doc/paper/supplements.tex

{\footnotesize\begin{longtable}{l l l l l}
    \caption[Line list of molecular test results over the study period]{Line list of respiratory cases over the study period. Viruses: Influenza B (Flu B), rhinovirus (HRV), adenovirus (AdV), SARS-CoV-2 (CoV), metapneumovirus (MPV), parainfluenza virus (PIV).}\label{tab:mol-data-line-list} \\
    \toprule
    Class & Date of test & Weekday & Test result & Virus \\
    \midrule
    \input ../../results/mol-data/line-list-data
    \bottomrule
\end{longtable}}

@@

\begin{figure}[!htpb]
    \centering
    \includegraphics{../../results/epi-data/incubation-periods.pdf}
    \caption[Choices of priors for the incubation periods]{Choices of priors for the distribution of the virus-specific incubation periods. Viruses: Influenza B (Flu B), rhinovirus (HRV), adenovirus (AdV), SARS-CoV-2 (CoV), metapneumovirus (MPV), parainfluenza virus (PIV).}
    \label{fig:prior-pin}
\end{figure}

>>>>

{\footnotesize\begin{longtable}{l l l l l}
    \caption[Line list of molecular test results over the study period]{Line list of respiratory cases over the study period. Flu B: Influenza B, HRV: rhinovirus, AdV: adenovirus, CoV: SARS-CoV-2, MPV: metapneumovirus, PIV: parainfluenza virus.}\label{tab:mol-data-line-list} \\
    \toprule
    Class & Date of test & Weekday & Test result & Virus \\
    \midrule
    \input ../../results/mol-data/line-list-data
    \bottomrule
\end{longtable}}

@@

\begin{figure}[!htpb]
    \centering
    \includegraphics{../../results/epi-data/incubation-periods.pdf}
    \caption[Choices of priors for the incubation periods]{Choices of priors for the distribution of the virus-specific incubation periods. Flu B: Influenza B, HRV: rhinovirus, AdV: adenovirus, CoV: SARS-CoV-2, MPV: metapneumovirus, PIV: parainfluenza virus.}
    \label{fig:prior-pin}
\end{figure}
